Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-03-01 manuscript/manuscript.Rmd
Moved plotting routines to separate script to maintain flow of manuscript better.

require(power.transform)
require(ggplot2)
require(data.table)
require(latex2exp)
require(coro)

manuscript_dir <- file.path("C:/Users/alexz/Documents/GitHub/power.transform/manuscript")
source(file.path(manuscript_dir, "simulations.R"))

@@

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)

get_annotation_settings <- function(ggtheme=NULL){
  # Import formatting settings from the provided ggtheme.

  # Find the text size for the table. This is based on text sizes in the
  # ggtheme.
  fontsize <- ggtheme$text$size
  fontsize_rel <- 1.0

  # Attempt to base the text size on the general axis.text attribute.
  if(!is.null(ggtheme$axis.text$size)){
    if(inherits(ggtheme$axis.text$size, "rel")){
      # Find the relative text size of axis text.
      fontsize_rel <- as.numeric(ggtheme$axis.text$size)

    } else {
      # Set absolute text size.
      fontsize <- ggtheme$axis.text$size
      fontsize_rel <- 1.0
    }
  }

  # Attempt to refine the text size using the axis.text.y attribute in
  # particular.
  if(!is.null(ggtheme$axis.text.y$size)){
    if(inherits(ggtheme$axis.text.y$size, "rel")){
      # Set relative text size of axis text
      fontsize_rel <- as.numeric(ggtheme$axis.text.y$size)

    } else {
      # Set absolute text size.
      fontsize <- as.numeric(ggtheme$axis.text.y$size)
      fontsize_rel <- 1.0
    }
  }

  # Update the text size using the magical ggplot2 point size (ggplot2:::.pt).
  geom_text_size <- fontsize * fontsize_rel / 2.845276

  # Obtain lineheight
  lineheight <- ggtheme$text$lineheight
  if(!is.null(ggtheme$axis.text$lineheight)) lineheight <- ggtheme$axis.text$lineheight
  if(!is.null(ggtheme$axis.text.y$lineheight)) lineheight <- ggtheme$axis.text.y$lineheight

  # Obtain family
  fontfamily <- ggtheme$text$family
  if(!is.null(ggtheme$axis.text$family)) fontfamily <- ggtheme$axis.text$family
  if(!is.null(ggtheme$axis.text.y$family)) fontfamily <- ggtheme$axis.text.y$family
  if(!is.null(ggtheme$axis.text.x$family)) fontfamily <- ggtheme$axis.text.x$family

  # Obtain face
  fontface <- ggtheme$text$face
  if(!is.null(ggtheme$axis.text$face)) fontface <- ggtheme$axis.text$face
  if(!is.null(ggtheme$axis.text.y$face)) fontface <- ggtheme$axis.text.y$face
  if(!is.null(ggtheme$axis.text.x$face)) fontface <- ggtheme$axis.text.x$face

  # Obtain colour
  colour <- ggtheme$text$colour
  if(!is.null(ggtheme$axis.text$colour)) colour <- ggtheme$axis.text$colour
  if(!is.null(ggtheme$axis.text.y$colour)) colour <- ggtheme$axis.text.y$colour
  if(!is.null(ggtheme$axis.text.x$colour)) colour <- ggtheme$axis.text.x$colour

  return(list(
    "geom_text_size"=geom_text_size,
    "fontsize"=fontsize,
    "fontsize_rel"=fontsize_rel,
    "colour"=colour,
    "family"=fontfamily,
    "face"=fontface,
    "lineheight"=lineheight))
}

@@

compute_lambda <- function(mu, x, method){
  # Create transformer object.
  transformer <- suppressWarnings(
    power.transform::find_transformation_parameters(
      x = x + mu,
      method = method,
      robust = FALSE,
      shift = FALSE,
      lambda = NULL,
      optimiser_control = list("xtol_rel"=1e-3)))

  # Return lambda value.
  return(transformer@lambda)
}

# Non-standard evaluation
mu <- lambda <- method <- NULL

x <- power.transform::ragn(10000L, location=0, scale=1/sqrt(2), alpha=0.5, beta=2)
shift_range <- 10^seq(from=0, to=6, by=0.1)

box_cox_values <- sapply(
  shift_range,
  compute_lambda,
  x = x,
  method = "box_cox")

yeo_johnson_values <- sapply(
  shift_range,
  compute_lambda,
  x = x,
  method = "yeo_johnson")

data <- data.table::data.table(
  "mu" = log10(c(shift_range, shift_range)),
  "lambda" = c(box_cox_values, yeo_johnson_values),
  "method" = factor(
    x=rep(
      c("Box-Cox", "Yeo-Johnson"),
      each = length(shift_range)),
    levels=c("Box-Cox", "Yeo-Johnson")))

annotation_settings <- get_annotation_settings(ggplot2::theme_light(base_size = base_size))

p_bc <- ggplot2::ggplot(
  data = data[method == "Box-Cox"],
  mapping = ggplot2::aes(
    x = mu,
    y = lambda,
    colour = method))
p_bc <- p_bc + plot_theme
p_bc <- p_bc + ggplot2::geom_point()
p_bc <- p_bc + ggplot2::geom_hline(
  yintercept = 1.0, 
  linetype="longdash", 
  colour="grey40")
p_bc <- p_bc + ggplot2::annotate(
  geom = "text",
  x = 6,
  y = 1,
  label = "expected",
  colour=annotation_settings$colour,
  family=annotation_settings$family,
  fontface=annotation_settings$face,
  size=annotation_settings$geom_text_size,
  vjust=-1.0,
  hjust=1.0)
p_bc <- p_bc + ggplot2::scale_x_continuous(
  name = latex2exp::TeX("$\\mu$"),
  labels = scales::math_format())
p_bc <- p_bc + ggplot2::scale_y_continuous(
  name = latex2exp::TeX("$\\lambda$"),
  limits = c(0.0, 35.0))
p_bc <- p_bc + paletteer::scale_color_paletteer_d(
  palette="ggthemes::Tableau_10",
  drop=FALSE,
  guide="none")

p_yj <- ggplot2::ggplot(
  data = data[method == "Yeo-Johnson"],
  mapping = ggplot2::aes(
    x = mu,
    y = lambda,
    colour = method))
p_yj <- p_yj + plot_theme
p_yj <- p_yj + ggplot2::geom_point()
p_yj <- p_yj + ggplot2::geom_hline(
  yintercept = 1.0,
  linetype="longdash",
  colour="grey40")
p_yj <- p_yj + ggplot2::annotate(
  geom = "text",
  x = 6,
  y = 1,
  label = "expected",
  colour=annotation_settings$colour,
  family=annotation_settings$family,
  fontface=annotation_settings$face,
  size=annotation_settings$geom_text_size,
  vjust=-1.0,
  hjust=1.0)
p_yj <- p_yj + ggplot2::scale_x_continuous(
  name = latex2exp::TeX("$\\mu$"),
  labels = scales::math_format())
p_yj <- p_yj + ggplot2::scale_y_continuous(
  name = latex2exp::TeX("$\\lambda$"),
  limits = c(0.0, 35.0))
p_yj <- p_yj + paletteer::scale_color_paletteer_d(
  palette="ggthemes::Tableau_10",
  drop=FALSE)
p_yj <- p_yj + ggplot2::theme(
  axis.title.y=ggplot2::element_blank(),
  axis.text.y=ggplot2::element_blank())

p <- egg::ggarrange(plots=list(p_bc, p_yj), ncol=2, draw=FALSE)
p
```

@@

# Non-standard evaluation
d <- distribution <- method <- mean_lambda <- sd_lambda <- estimation_method <- NULL

# Density plot.
.create_density_plot <- function(x, plot_theme, limits=c(-5, 5)){
  p <- ggplot2::ggplot(
    data = data.table::data.table("x"=x),
    mapping = ggplot2::aes(
      x = x))
  p <- p + plot_theme
  p <- p + ggplot2::geom_density()
  p <- p + ggplot2::theme(
    axis.title = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    panel.grid = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    plot.title=ggplot2::element_text(
      hjust=0.5,
      size=ggplot2::rel(1.0)))
  p <- p + ggplot2::xlim(limits)

# Lambda plot,
.create_lambda_shift_plot <- function(data, plot_theme, limits, guide=FALSE){

  p <- ggplot2::ggplot(
    data = data,
    mapping = ggplot2::aes(
      x = d,
      y = lambda,
      colour = method,
      shape = version))
  p <- p + plot_theme
  p <- p + ggplot2::geom_point()
  p <- p + ggplot2::scale_x_continuous(
    name = latex2exp::TeX("$d$"),
    labels = scales::math_format())
  p <- p + ggplot2::scale_y_continuous(
    name = latex2exp::TeX("$\\lambda$"),
    limits = limits)

  if(guide){
    p <- p + paletteer::scale_color_paletteer_d(
      palette = "ggthemes::Tableau_10",
      drop = FALSE)

  } else {
    p <- p + paletteer::scale_color_paletteer_d(
      palette = "ggthemes::Tableau_10",
      drop = FALSE,
      guide = "none")
    p <- p + ggplot2::scale_shape_discrete(guide="none")
  }

# Load data.
data <- .get_shifted_distribution_data(manuscript_dir=manuscript_dir)
data[estimation_method == "MLE"]

#### Normal distribution -------------------------------------------------------
# Density
p_dens_normal <- .create_density_plot(
  x = x_normal,
  plot_theme = plot_theme)
p_dens_normal <- p_dens_normal + ggplot2::ggtitle(label="normal distribution")

# Box-Cox
p_bc_normal <- .create_lambda_shift_plot(
  data = data[distribution == "normal" & method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(0.0, 35.0))

# Yeo-Johnson
p_yj_normal <- .create_lambda_shift_plot(
  data=data[distribution == "normal" & method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(0.0, 35.0))

#### Right skewed distribution -------------------------------------------------

# Density
p_dens_right <- .create_density_plot(
  x = x_right_skewed,
  plot_theme = plot_theme)
p_dens_right <- p_dens_right + ggplot2::ggtitle(label="right-skewed distribution")

# Box-Cox
p_bc_right <- .create_lambda_shift_plot(
  data = data[distribution == "right-skewed" & method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(-9.0, 1.0))

# Yeo-Johnson
p_yj_right <- .create_lambda_shift_plot(
  data = data[distribution == "right-skewed" & method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-9.0, 1.0))

#### Left skewed distribution --------------------------------------------------

# Density
p_dens_left <- .create_density_plot(
  x = x_left_skewed,
  plot_theme = plot_theme)
p_dens_left <- p_dens_left + ggplot2::ggtitle(label="left-skewed distribution")

# Box-Cox
p_bc_left <- .create_lambda_shift_plot(
  data = data[distribution == "left-skewed" & method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(0.0, 60.0),
  guide = TRUE)

# Yeo-Johnson
p_yj_left <- .create_lambda_shift_plot(
  data = data[distribution == "left-skewed" & method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(0.0, 60.0))

#### Aggregate -----------------------------------------------------------------

aggregate_data <- data[, list("mean_lambda"=mean(lambda), "sd_lambda"=stats::sd(lambda)), by=c("method", "version", "distribution")]
aggregate_data$distribution <- factor(
  x=aggregate_data$distribution,
  levels = c("normal", "left-skewed", "right-skewed"))
aggregate_data[, "text":=parse_mean_sd_latex(mu=mean_lambda, sigma=sd_lambda)]

p <- egg::ggarrange(
  plots=list(
    p_dens_normal, p_bc_normal, p_yj_normal,
    p_dens_right, p_bc_right, p_yj_right,
    p_dens_left, p_bc_left, p_yj_left),
  ncol=3,
  heights=c(0.5, 1.0, 1.0),
  byrow=FALSE,
  draw=FALSE)
p
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
two_sided_function_parameters <- .get_optimised_weighting_function_parameters_two_sided(manuscript_dir = manuscript_dir)

```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
two_sided_transformation_parameters <- .get_transformation_parameters_two_sided(manuscript_dir = manuscript_dir)

@@

Each of the criteria above can be used for optimisation, i.e.:

@@

@@

# Lambda plot,
.create_lambda_shift_plot <- function(data, plot_theme, limits, guide=FALSE){

  p <- ggplot2::ggplot(
    data = data,
    mapping = ggplot2::aes(
      x = d,
      y = lambda,
      colour = estimation_method))
  p <- p + plot_theme
  p <- p + ggplot2::geom_point()
  p <- p + ggplot2::scale_x_continuous(
    name = latex2exp::TeX("$d$"),
    labels = scales::math_format())
  p <- p + ggplot2::scale_y_continuous(
    name = latex2exp::TeX("$\\lambda$"),
    limits = limits)
  p <- p + ggplot2::theme(
    plot.title=ggplot2::element_text(
      hjust=0.5,
      size=ggplot2::rel(1.0)))

  if(guide){
    p <- p + paletteer::scale_color_paletteer_d(
      palette = "ggthemes::Tableau_10",
      drop = FALSE)
    p <- p + guides(colour = ggplot2::guide_legend(title = "Optimisation criterion"))

  } else {
    p <- p + paletteer::scale_color_paletteer_d(
      palette = "ggthemes::Tableau_10",
      drop = FALSE,
      guide = "none")
  }

data <- .get_shifted_distribution_data(manuscript_dir = manuscript_dir)

#### Normal distribution -------------------------------------------------------

# Box-Cox-original
p_bc_normal <- .create_lambda_shift_plot(
  data = data[distribution == "normal" & method == "Box-Cox" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-20.0, 35.0))
p_bc_normal <- p_bc_normal + ggplot2::ggtitle(label="normal distribution")

# Yeo-Johnson
p_yj_normal <- .create_lambda_shift_plot(
  data=data[distribution == "normal" & method == "Yeo-Johnson" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-20.0, 35.0))

#### Right skewed distribution -------------------------------------------------

# Box-Cox
p_bc_right <- .create_lambda_shift_plot(
  data = data[distribution == "right-skewed" & method == "Box-Cox" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-15.0, 1.0))
p_bc_right <- p_bc_right + ggplot2::ggtitle(label="right-skewed distribution")

# Yeo-Johnson
p_yj_right <- .create_lambda_shift_plot(
  data = data[distribution == "right-skewed" & method == "Yeo-Johnson" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-15.0, 1.0))

#### Left skewed distribution --------------------------------------------------

# Box-Cox
p_bc_left <- .create_lambda_shift_plot(
  data = data[distribution == "left-skewed" & method == "Box-Cox" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-50.0, 60.0),
  guide = TRUE)
p_bc_left <- p_bc_left + ggplot2::ggtitle(label="left-skewed distribution")

# Yeo-Johnson
p_yj_left <- .create_lambda_shift_plot(
  data = data[distribution == "left-skewed" & method == "Yeo-Johnson" & version == "original"],
  plot_theme = plot_theme,
  limits = c(-50.0, 60.0))

p <- egg::ggarrange(
  plots=list(
    p_bc_normal, p_yj_normal,
    p_bc_right, p_yj_right,
    p_bc_left, p_yj_left),
  ncol=3,
  heights=c(1.0, 1.0),
  byrow=FALSE,
  draw=FALSE)
p

p <- ggplot2::ggplot(
  data = data,
  mapping = ggplot2::aes(
    x = d,
    y = lambda,
    colour = estimation_method))
p <- p + plot_theme
p <- p + ggplot2::geom_point()
p <- p + ggplot2::scale_x_continuous(
  name = latex2exp::TeX("$d$"),
  labels = scales::math_format())
p <- p + ggplot2::scale_y_continuous(
  name = latex2exp::TeX("$\\lambda$"))
p <- p + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE)
p <- p + guides(colour = ggplot2::guide_legend(title = "optimisation criterion"))

p <- p + ggplot2::facet_grid(
  method + version ~ distribution,
  scales = "free")

>>>>

require(power.transform)
require(ggplot2)
require(patchwork)
require(data.table)
require(latex2exp)
require(coro)

manuscript_dir <- file.path("C:/Users/alexz/Documents/GitHub/power.transform/manuscript")
source(file.path(manuscript_dir, "simulations.R"))
source(file.path(manuscript_dir, "plots.R"))

@@

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")

@@

.plot_reduced_normality(plot_theme = plot_theme, manuscript_dir = manuscript_dir)

@@

.plot_shifted_distributions(manuscript_dir = manuscript_dir, plot_theme = plot_theme)
```

@@

```{r optimal_criteria, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Things."
)

# This find the optimal weighting parameter settings that are used within the
# package.
two_sided_function_parameters <- .get_optimised_weighting_function_parameters_two_sided(manuscript_dir = manuscript_dir)

# This finds lambda values at the optimised weighting parameter settings.
data <- .get_transformation_parameters_two_sided(manuscript_dir = manuscript_dir)

data <- data[estimation_method == "MLE"]
data <- data[, "lambda_error" := abs(lambda - target_lambda)]
non_robust_data <- data[weight_method == "non-robust", mget(c("method", "estimation_method", "k", "ii", "lambda_error"))]
data[non_robust_data, on=c("method", "estimation_method", "k", "ii"), "non_robust_lambda_error" := i.lambda_error]

data[, "better_than_non_robust" := lambda_error <= non_robust_lambda_error]
data[k == 0.0, "better_than_non_robust" := NA_integer_]
data[weight_method == "non-robust", "better_than_non_robust" := NA_integer_]

pass_rate_data <- data[, list(
  "pass_rate" = sum(better_than_non_robust, na.rm=TRUE),
  "n" = sum(!is.na(better_than_non_robust)),
  "median_error" = stats::median(lambda_error)),
  by=c("method", "estimation_method", "weight_method")]
pass_rate_data[, "pass_rate" := round(pass_rate / n * 100.0, 1)][order(pass_rate)]

p <- ggplot2::ggplot(
  data = data,
  mapping = ggplot2::aes(
    x = weight_method,
    y = lambda_error,
    fill = method))
p <- p + plot_theme
p <- p + ggplot2::geom_violin(draw_quantiles = 0.5)
p <- p + ggplot2::facet_wrap("method", nrow=2)
p <- p + paletteer::scale_fill_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE)
p <- p + ggplot2::scale_y_sqrt(name = latex2exp::TeX("$| \\hat{\\lambda}^r - \\hat{\\lambda}_{0}|$"))
p <- p + ggplot2::xlab("weighting method")
p <- p + ggplot2::theme(
  axis.text.x = ggplot2::element_text(
    angle=60.0,
    hjust=1.0))

@@

Each of the criteria described in the previous section can be used for optimisation, i.e.:

@@

# Appendix B: Simulations with other optimisation criteria

@@

  .plot_shifted_distributions_other_criteria(manuscript_dir = manuscript_dir, plot_theme = plot_theme)
```

```{r optimal_weighting_function_all_criteria_box_cox, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Things."
)
# This finds lambda values at the optimised weighting parameter settings.
data <- .get_transformation_parameters_two_sided(manuscript_dir = manuscript_dir)

data <- data[method == "Box-Cox"]
data <- data[, "lambda_error" := abs(lambda - target_lambda)]
non_robust_data <- data[weight_method == "non-robust", mget(c("method", "estimation_method", "k", "ii", "lambda_error"))]
data[non_robust_data, on=c("method", "estimation_method", "k", "ii"), "non_robust_lambda_error" := i.lambda_error]

data[, "better_than_non_robust" := lambda_error <= non_robust_lambda_error]
data[k == 0.0, "better_than_non_robust" := NA_integer_]
data[weight_method == "non-robust", "better_than_non_robust" := NA_integer_]

pass_rate_data <- data[, list(
  "pass_rate" = sum(better_than_non_robust, na.rm=TRUE),
  "n" = sum(!is.na(better_than_non_robust)),
  "median_error" = stats::median(lambda_error)),
  by=c("method", "estimation_method", "weight_method")]
pass_rate_data <- pass_rate_data[, "pass_rate" := round(pass_rate / n * 100.0, 1)]

p <- ggplot2::ggplot(
  data = data,
  mapping = ggplot2::aes(
    x = weight_method,
    y = lambda_error,
    fill = estimation_method))
p <- p + plot_theme
p <- p + ggplot2::geom_violin(draw_quantiles = 0.5)
p <- p + ggplot2::facet_wrap("estimation_method", nrow=nlevels(data$estimation_method))
p <- p + paletteer::scale_fill_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE)
p <- p + ggplot2::scale_y_sqrt(name = latex2exp::TeX("$| \\hat{\\lambda}^r - \\hat{\\lambda}_{0}|$"))
p <- p + ggplot2::xlab("weighting method")
p <- p + ggplot2::ggtitle("shift-sensitive Box-Cox transformation")
p <- p + ggplot2::theme(
  axis.text.x = ggplot2::element_text(
    angle=30.0,
    hjust=1.0))
p
```

```{r optimal_weighting_function_all_criteria_yeo_johnson, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Things."
)
# This finds lambda values at the optimised weighting parameter settings.
data <- .get_transformation_parameters_two_sided(manuscript_dir = manuscript_dir)

data <- data[method == "Yeo-Johnson"]
data <- data[, "lambda_error" := abs(lambda - target_lambda)]
non_robust_data <- data[weight_method == "non-robust", mget(c("method", "estimation_method", "k", "ii", "lambda_error"))]
data[non_robust_data, on=c("method", "estimation_method", "k", "ii"), "non_robust_lambda_error" := i.lambda_error]

data[, "better_than_non_robust" := lambda_error <= non_robust_lambda_error]
data[k == 0.0, "better_than_non_robust" := NA_integer_]
data[weight_method == "non-robust", "better_than_non_robust" := NA_integer_]

pass_rate_data <- data[, list(
  "pass_rate" = sum(better_than_non_robust, na.rm=TRUE),
  "n" = sum(!is.na(better_than_non_robust)),
  "median_error" = stats::median(lambda_error)),
  by=c("method", "estimation_method", "weight_method")]
pass_rate_data[, "pass_rate" := round(pass_rate / n * 100.0, 1)][order(pass_rate)]

p <- ggplot2::ggplot(
  data = data,
  mapping = ggplot2::aes(
    x = weight_method,
    y = lambda_error,
    fill = estimation_method))
p <- p + plot_theme
p <- p + ggplot2::geom_violin(draw_quantiles = 0.5)
p <- p + ggplot2::facet_wrap("estimation_method", nrow=nlevels(data$estimation_method))
p <- p + paletteer::scale_fill_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE)
p <- p + guides(fill = ggplot2::guide_legend(title = "optimisation criterion"))
p <- p + ggplot2::scale_y_sqrt(name = latex2exp::TeX("$| \\hat{\\lambda}^r - \\hat{\\lambda}_{0}|$"))
p <- p + ggplot2::xlab("weighting method")
p <- p + ggplot2::ggtitle("shift-sensitive Yeo-Johnson transformation")
p <- p + ggplot2::theme(
  axis.text.x = ggplot2::element_text(
    angle=30.0,
    hjust=1.0))
p
